### 2014-02-25 paper/retrofit.tex
Caps
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Proof checkpoint.

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = {it2, ..., it1}
  sched done (it1, it2, ...)    = {it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched fork (it1, it2, ...)    = {it2, ..., it1}
\end{code}
  Browbound:
\begin{code}
  sched step (it1, it2, ...)    = {it1, it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched done (it1, it2, ...)    = {it2, ...}
  sched fork (it1, it2, ...)    = {it1, it2, ...}
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ...)       = {it1, it2, ...}
  sched noStep (it1, it2, ...)     = {it1, it2, ...}
  sched done (it1, it2, ...)       = {it2, ...}
  sched fork (it1, it2, ... it1n)  = {itn, it1, it2, ...}
\end{code}
\caption{scheduling policies}
\end{figure}

@@

    Therefore, after |its2| has potentially executed some number of steps
    to arrive at |its2''|, we are now in the situation where $|its1|\approx_{|il|}|its2''|$, and the first task |it1| and |it2| don't
    get erased and are |il| equivalent.  We consider all
    possible rules used to derive~\eqref{eq:tsni-lemma-lhs}:
    \begin{description}
      \item[Case \textsc{I-done}] 
      \item[Case \textsc{I-noStep}] 
      \item[Case \textsc{I-fork}] 
      \item[Case \textsc{I-setLabel}]
    \end{description}
  \end{itemize}
\end{proof}

>>>>

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = {it2, ..., it1}
  sched done (it1, it2, ...)    = {it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched fork (it1, it2, ...)    = {it2, ..., it1}
\end{code}
  Browbound:
\begin{code}
  sched step (it1, it2, ...)    = {it1, it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched done (it1, it2, ...)    = {it2, ...}
  sched fork (it1, it2, ...)    = {it1, it2, ...}
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ...)       = {it1, it2, ...}
  sched noStep (it1, it2, ...)     = {it1, it2, ...}
  sched done (it1, it2, ...)       = {it2, ...}
  sched fork (it1, it2, ... it1n)  = {itn, it1, it2, ...}
\end{code}
\caption{Scheduling policies}
\end{figure}

@@

    Therefore, after |its2| has potentially executed some number of steps
    to arrive at |its2''|, we are now in the situation where $|its1|\approx_{|il|}|its2''|$, and the first task |it1| and |it2| don't
    get erased and are |il| equivalent.
    We consider all
    possible rules used to derive~\eqref{eq:tsni-lemma-lhs}:
    \begin{description}
      \item[Case \textsc{I-setLabel}]
        From the form of the rule we know that the expression |ie1| executing
        in task |it1| is of the form |iniE (setLabel il)|.
        If |it2| is also of the form |iniE' (setLabel il)| for some
        |iniE'| that is |il| equivalent to |iniE|,
        then~\eqref{eq:tsni-lemma-rhs}
        holds by executing the same step.
        Otherwise, if the two are not syntactically equivalent, then
        |it1| must contain a |send| that gets erased by |erasef il|, and
        must currently be executing the part that got erased.
        \Red{this reasoning is not actually right.  will be fixed shortly.}
      \item[Case \textsc{I-done}] 
      \item[Case \textsc{I-noStep}] 
      \item[Case \textsc{I-fork}] 
    \end{description}
  \end{itemize}
\end{proof}
